### 2021-10-22 documentos/vector_space.tex
Derp

Other two simple but crucial
observation are the following. For valid quantum channels, 
% \begin{equation}
% % \sum_{
% \end{equation}
$\sum_{\valpha \in \Omega} \lambda_\valpha=0$ implies that 
$\lambda_\valpha=0$ for all $\valpha$ in an arbitrary subset of 
multi-indices $\Omega$, as each member of the sum is
greater or equal to zero, 
% $p_{\vec\alpha}+p_{\vec\beta}=0$ implies $p_{\vec\alpha}=p_{\vec\beta}=0$, as
% all $p_{\vec\alpha} \ge 0$
due to complete positivity of the underlying channel. 
Finally, looking into the first component of \eref{eq:tau:is:A:p}, and taking into 
account the normalization condition that $\tau_{\vec 0}=1$, we obtain
\begin{equation}
\sum_\valpha \lambda_\valpha = 2^N,
\label{eq:sum:alpha:is:2N}
\end{equation}
since, $A_{\vec 0, \vbeta}=1$ for all $\vbeta$. \par
% }}}
% Conexion de los indices para llegar al grupo de Klein {{{
Now we need a definition: to each multi-index $\vec\alpha$ we associate a \textit{set}
of multi-indices $\Phi(\vec\alpha)$ as follows
\begin{equation}
\Phi(\vec\alpha):=\left\{
\vec\beta:\san_{\vec\alpha\vec\beta}=1
\right\}
% =\left\{ \vec\beta: \sa_{\alpha_1\beta_1}\cdot\ldots\cdot \sa_{\alpha_N\beta_N}
% =1
% \right\}
\label{eq:8}
\end{equation}
% If we now assume that $\tau_{\vec\alpha}=1$, it follows from subtracting 
If we now assume that $\tau_{\vec\alpha}=1$, and calculate the difference between
\eref{eq:sum:alpha:is:2N} and
$\sum_{\vec\beta}\san_{\vec\alpha\vec\beta}\lambda_{\vec\beta}=2^N$
(which follows from the aforementioned assumption), one obtains
% \begin{subequations}
% \begin{eqnarray}
% \sum_{\vec\beta}p_{\vec\beta}&=&1
% \label{eq:9a}\\
% \sum_{\vec\beta}\san_{\vec\alpha\vec\beta}p_{\vec\beta}&=&\tau_{\vec\alpha}=1
% \end{eqnarray}
% \label{eq:9}
% \end{subequations}
% that for all $\vec\beta\notin\Phi(\vec\alpha)$
\begin{eqnarray}
\lambda_{\vec\beta}=0,\quad \forall \vec\beta\notin\Phi(\vec\alpha).
\label{eq:condition:lambda:zero:Phi}
\end{eqnarray}
Thus, if $\tau_{\vec\alpha}=1$, then $\tau_{\vec\gamma}$
and $\tau_{\vec{\gamma^\prime}}$ are equal if
% , for all $\vec\beta\in\Phi(\vec\alpha)$.
\begin{equation}
\san_{\vbeta\vec\gamma}=\san_{\vbeta\vec{\gamma^\prime}}, \quad
\forall \vec\beta\in\Phi(\vec\alpha).
\label{eq:coneccion:dos:indices:A}
\end{equation}
% holds for all $\vec\beta\in\Phi(\vec\alpha)$. 
This follows from restricting the sum \eref{eq:tau:is:A:p}
to the $\lambda_\vbeta \ne 0$, given in \eref{eq:condition:lambda:zero:Phi}. 
Condition (\ref{eq:coneccion:dos:indices:A}) therefore connects three
multi-indices, $\valpha$,
$\vec\gamma$ and $\vec{\gamma^\prime}$.
When such a connection exists, $\tau_{\vec\alpha}=1$ implies
$\tau_{\vec\gamma}=\tau_{\vec{\gamma^\prime}}$. Let us now work out the nature
of this connection.

Let the components of  $\vbeta$ be such that $\beta_l = \beta \delta_{lk}$ for
a particular particle index $k$, with 
$\beta$ such that $\sa_{\alpha_k\beta}=1$.
Since $\sa_{\alpha 0}=1$ for any $\alpha$, this particular election of $\vbeta$
belongs to  $\Phi(\vec\alpha)$, so that \eref{eq:coneccion:dos:indices:A}
indeed holds. However, for such election of $\vbeta$ the above relation reduces
to 
\begin{equation}
\sa_{\beta\gamma_k}=\sa_{\beta\gamma_k^\prime}
\label{eq:14}
\end{equation}
for all $\beta$ such that $\sa_{{\alpha_k}\beta}=1$. 
One can verify, by working out the different cases, 
that \eref{eq:14} is equivalently expressed as 
\begin{equation}
\gamma_k^\prime=\alpha_k\oplus{}\gamma_k
\label{eq:oplus}
\end{equation}
where the $\oplus{}$ denotes the operation of the Klein group; see Figure
\ref{tab:1} for a detailed description. 
\par
% 
% 
% % Since all elements of $A$ are $\pm1$, and using that $A_{\valpha \vbeta}=1$
% % of $\vbeta \in \Phi(\vec\alpha)$, we may rewrite \eref{eq:coneccion:dos:indices:A}
% % as
% % \begin{equation}
% % \san_{\vbeta\vec\gamma} \san_{\vbeta\vec{\gamma^\prime}} 
% % = 
% % 1
% % , \quad
% % \forall \vec\beta\in\Phi(\vec\alpha),
% % \label{eq:12}
% % \end{equation}
% % which can be further decomposed in 
% % \begin{equation}
% % \sa_{\beta_1\gamma_1}\sa_{\beta_1\gamma_1^\prime}
% %   \ldots
% % %   \cdot\ldots\cdot 
% % \sa_{\beta_N\gamma_N}\sa_{\beta_N\gamma_N^\prime}=1.
% % \label{eq:13}
% % \end{equation}
% % Moreover, since 
% % 
% % 
% % 
% % Since $\sa_{\alpha\beta}=\pm1$, we may rewrite (\ref{eq:11}) as
% % \begin{equation}
% % \sa_{\beta_1\gamma_1}\sa_{\beta_1\gamma_1^\prime}\cdot\ldots\cdot \sa_{\beta_N\gamma_N}\sa_{\beta_N\gamma_N^\prime}=1.
% % \label{eq:12}
% % \end{equation}
% % This must hold for all $\vec\beta\in\Phi(\vec\alpha)$. From this follows that
% % (\ref{eq:12}) may be rewritten as
% % \begin{equation}
% % \sa_{\beta_1\gamma_1}\sa_{\beta_1\gamma_1^\prime}\cdot\ldots\cdot \sa_{\beta_N\gamma_N}\sa_{\beta_N\gamma_N^\prime}=
% % \sa_{\alpha_1\beta_1}\cdot\ldots\cdot \sa_{\alpha_N\beta_N}.
% % \label{eq:13}
% % \end{equation}
% % Here we show that (\ref{eq:13}) implies (\ref{eq:14}). 
% Since \eref{eq:13} holds for 
% all $\vec\beta\in\Phi(\vec\alpha)$, we may choose a specific such $\vec\beta$, namely
% $\beta_l=0$ for all $l\neq k$ and $\beta_k=\beta$, where $\beta$ is an arbitrary number
% such that
% $\sa_{\alpha_k\beta}=1$. 
% % \begin{equation}
% % \sa_{\alpha_k\beta}=1.
% % \end{equation}
% This $\vec\beta$, as is readily verified, belongs to $\Phi(\vec\alpha)$, so
% that \eref{eq:13} indeed holds for this $\vec\beta$. On the other hand, it is
% then readily verified that, for this $\vec\beta$, \eref{eq:13} reduces to 
% % (\ref{eq:14}), whcih therefore follows. 
% % \flnote{Leve modificaci\'on de las ecuaciones anteriores, y adecuaci\'on del
% % texto siguiente. } \cpnote{francois, recuerdo 
% % que esto lo discutimos. No se si en el momento me convencí, pero ahora no veo 
% % proque se tiene que cumplir para los indices individulaes}. 
% % We now show in Appendix
% % \ref{app:proof} that from this follows that
% % for all $1\leq k\leq N$, $\gamma_k$
% % and $\gamma_k^\prime$ are connected by
% \begin{equation}
% \sa_{\beta\gamma_k}\sa_{\beta\gamma_k^\prime}=1
% \label{eq:14}
% \end{equation}
% for all $\beta$ such that $\sa_{{\alpha_k}\beta}=1$. 
% One can verify, by working out the different cases, 
% that \eref{eq:14} is equivalently expressed as 
% \begin{equation}
% \gamma_k^\prime=\alpha_k\oplus{}\gamma_k
% \label{eq:oplus}
% \end{equation}
% where the $\oplus{}$ denotes the operation of the Klein group; see Figure
% \ref{tab:1} for a detailed description. 
% \par
% }}}
% Espacio vectorial {{{

It will be useful to think of the multi-index $\valpha$ as an element of 
a vector space. To do so, we notice that any group with the property that
$\alpha \oplus \alpha =0$ is indeed a vector space under the two-element field
$\{0,1\}$\cite{alguna:referencia}.  Then, we build the complete vector space,
with the same field, and defining $\valpha \oplus \vbeta = (\alpha_1 \oplus
\beta_1,\cdots, \alpha_N \oplus \beta_N)$
\footnote{
We can further \cpnote{desmechar} the vector space, by identifying each index
$\alpha \in \{0,1,2,3\}$ with its binary notation [e.g. identify $2$ with $(1,0)$]
such that to each multindex  $\valpha$ there corresponds a binary string of 
length $2N$. In fact, our sum $\oplus$ would correspond to addition modulo 2 of 
each of the $2N$ components. 
}. 
We can indeed restate \eref{eq:oplus}, and say that for valid quantum channels, 
if $\tau_{\vec\alpha}=1$, then
$\tau_{\vec\gamma}=\tau_{\vec\alpha\oplus{}\vec\gamma}$.
For example, in \fref{fig:two:qubit:examples}(c) the indices that 
correspond to preserved components are 
$\valpha^{(0)} = (0,0)$, 
$\valpha^{(1)} = (0,2)$, 
$\valpha^{(2)} = (1,0)$, 
$\valpha^{(3)} = (2,2)$, and
$\valpha^{(4)} = (3,2)$. However, 
$\valpha^{(1)} + \valpha^{(2)} = (1,2)$, which is not preserved and thus this 
diagram does not correspond to a quantum channel.  From this view 
we can derive several interesting observations that will be presented in 
the rest of the section.

>>>>

Other two simple but crucial
observation are the following. For valid quantum channels, 
% \begin{equation}
% % \sum_{
% \end{equation}
% $\sum_{\valpha \in \Omega} \lambda_\valpha=0$ implies that 
% $\lambda_\valpha=0$ for all $\valpha$ in an arbitrary subset of 
% multi-indices $\Omega$, 
\begin{equation}
\sum_{\valpha \in \Omega} \lambda_\valpha=0 
\quad \implies 
\quad 
\lambda_\valpha=0, \, \forall \valpha \in \Omega
\label{eq:lambda:is:zero}
\end{equation}
for an arbitrary subset of multi-indices $\Omega$, 
as each member of the sum is
greater or equal to zero, 
due to complete positivity of the underlying channel. 
Finally, looking into the first component of \eref{eq:tau:is:A:p}, and taking into 
account the normalization condition that $\tau_{\vec 0}=1$, we obtain
\begin{equation}
\sum_\valpha \lambda_\valpha = 2^N,
\label{eq:sum:alpha:is:2N}
\end{equation}
since, $A_{\vec 0, \vbeta}=1$ for all $\vbeta$. \par
% }}}
% Conexion de los indices para llegar al grupo de Klein {{{
Now we need a definition: to each multi-index $\vec\alpha$ we associate a \textit{set}
of multi-indices $\Phi(\vec\alpha)$ as follows
\begin{equation}
\Phi(\vec\alpha):=\left\{
\vec\beta:\san_{\vec\alpha\vec\beta}=1
\right\}
% =\left\{ \vec\beta: \sa_{\alpha_1\beta_1}\cdot\ldots\cdot \sa_{\alpha_N\beta_N}
% =1
% \right\}
\label{eq:8}
\end{equation}
% If we now assume that $\tau_{\vec\alpha}=1$, it follows from subtracting 
If we now assume that $\tau_{\vec\alpha}=1$, and calculate the difference between
\eref{eq:sum:alpha:is:2N} and
$\sum_{\vec\beta}\san_{\vec\alpha\vec\beta}\lambda_{\vec\beta}=2^N$
(which follows from \eref{eq:tau:is:A:p} and $\tau_{\vec\alpha}=1$), one obtains
% \begin{subequations}
% \begin{eqnarray}
% \sum_{\vec\beta}p_{\vec\beta}&=&1
% \label{eq:9a}\\
% \sum_{\vec\beta}\san_{\vec\alpha\vec\beta}p_{\vec\beta}&=&\tau_{\vec\alpha}=1
% \end{eqnarray}
% \label{eq:9}
% \end{subequations}
% that for all $\vec\beta\notin\Phi(\vec\alpha)$
\begin{eqnarray}
\lambda_{\vec\beta}=0,\quad \forall \vec\beta\notin\Phi(\vec\alpha).
\label{eq:condition:lambda:zero:Phi}
\end{eqnarray}
Thus, if $\tau_{\vec\alpha}=1$, then $\tau_{\vec\gamma}$
and $\tau_{\vec{\gamma^\prime}}$ are equal if
% , for all $\vec\beta\in\Phi(\vec\alpha)$.
\begin{equation}
\san_{\vbeta\vec\gamma}=\san_{\vbeta\vec{\gamma^\prime}}, \quad
\forall \vec\beta\in\Phi(\vec\alpha).
\label{eq:coneccion:dos:indices:A}
\end{equation}
This follows from restricting the sum \eref{eq:tau:is:A:p}
to the $\lambda_\vbeta \ne 0$, given in \eref{eq:condition:lambda:zero:Phi}. 
Condition (\ref{eq:coneccion:dos:indices:A}) therefore connects three
multi-indices, $\valpha$,
$\vec\gamma$ and $\vec{\gamma^\prime}$.
When such a connection exists, $\tau_{\vec\alpha}=1$ implies
$\tau_{\vec\gamma}=\tau_{\vec{\gamma^\prime}}$. Let us now work out the nature
of this connection.

Let the components of  $\vbeta$ be such that $\beta_l = \beta \delta_{lk}$ for
a particular particle index $k$, with 
$\beta$ such that $\sa_{\alpha_k\beta}=1$.
Since $\sa_{\alpha 0}=1$ for any $\alpha$, this particular choice of $\vbeta$
belongs to  $\Phi(\vec\alpha)$, so that \eref{eq:coneccion:dos:indices:A}
indeed holds. However, for such election of $\vbeta$ the above relation reduces
to 
\begin{equation}
\sa_{\beta\gamma_k}=\sa_{\beta\gamma_k^\prime}
\label{eq:14}
\end{equation}
for all $\beta$ such that $\sa_{{\alpha_k}\beta}=1$. 
One can verify, by working out the different cases, 
that \eref{eq:14} is equivalently expressed as 
\begin{equation}
\gamma_k^\prime=\alpha_k\oplus{}\gamma_k
\label{eq:oplus}
\end{equation}
where the $\oplus{}$ denotes the operation of the Klein group; see Figure
\ref{tab:1} for a detailed description. 
\par
% 
% 
% % Since all elements of $A$ are $\pm1$, and using that $A_{\valpha \vbeta}=1$
% % of $\vbeta \in \Phi(\vec\alpha)$, we may rewrite \eref{eq:coneccion:dos:indices:A}
% % as
% % \begin{equation}
% % \san_{\vbeta\vec\gamma} \san_{\vbeta\vec{\gamma^\prime}} 
% % = 
% % 1
% % , \quad
% % \forall \vec\beta\in\Phi(\vec\alpha),
% % \label{eq:12}
% % \end{equation}
% % which can be further decomposed in 
% % \begin{equation}
% % \sa_{\beta_1\gamma_1}\sa_{\beta_1\gamma_1^\prime}
% %   \ldots
% % %   \cdot\ldots\cdot 
% % \sa_{\beta_N\gamma_N}\sa_{\beta_N\gamma_N^\prime}=1.
% % \label{eq:13}
% % \end{equation}
% % Moreover, since 
% % 
% % 
% % 
% % Since $\sa_{\alpha\beta}=\pm1$, we may rewrite (\ref{eq:11}) as
% % \begin{equation}
% % \sa_{\beta_1\gamma_1}\sa_{\beta_1\gamma_1^\prime}\cdot\ldots\cdot \sa_{\beta_N\gamma_N}\sa_{\beta_N\gamma_N^\prime}=1.
% % \label{eq:12}
% % \end{equation}
% % This must hold for all $\vec\beta\in\Phi(\vec\alpha)$. From this follows that
% % (\ref{eq:12}) may be rewritten as
% % \begin{equation}
% % \sa_{\beta_1\gamma_1}\sa_{\beta_1\gamma_1^\prime}\cdot\ldots\cdot \sa_{\beta_N\gamma_N}\sa_{\beta_N\gamma_N^\prime}=
% % \sa_{\alpha_1\beta_1}\cdot\ldots\cdot \sa_{\alpha_N\beta_N}.
% % \label{eq:13}
% % \end{equation}
% % Here we show that (\ref{eq:13}) implies (\ref{eq:14}). 
% Since \eref{eq:13} holds for 
% all $\vec\beta\in\Phi(\vec\alpha)$, we may choose a specific such $\vec\beta$, namely
% $\beta_l=0$ for all $l\neq k$ and $\beta_k=\beta$, where $\beta$ is an arbitrary number
% such that
% $\sa_{\alpha_k\beta}=1$. 
% % \begin{equation}
% % \sa_{\alpha_k\beta}=1.
% % \end{equation}
% This $\vec\beta$, as is readily verified, belongs to $\Phi(\vec\alpha)$, so
% that \eref{eq:13} indeed holds for this $\vec\beta$. On the other hand, it is
% then readily verified that, for this $\vec\beta$, \eref{eq:13} reduces to 
% % (\ref{eq:14}), whcih therefore follows. 
% % \flnote{Leve modificaci\'on de las ecuaciones anteriores, y adecuaci\'on del
% % texto siguiente. } \cpnote{francois, recuerdo 
% % que esto lo discutimos. No se si en el momento me convencí, pero ahora no veo 
% % proque se tiene que cumplir para los indices individulaes}. 
% % We now show in Appendix
% % \ref{app:proof} that from this follows that
% % for all $1\leq k\leq N$, $\gamma_k$
% % and $\gamma_k^\prime$ are connected by
% \begin{equation}
% \sa_{\beta\gamma_k}\sa_{\beta\gamma_k^\prime}=1
% \label{eq:14}
% \end{equation}
% for all $\beta$ such that $\sa_{{\alpha_k}\beta}=1$. 
% One can verify, by working out the different cases, 
% that \eref{eq:14} is equivalently expressed as 
% \begin{equation}
% \gamma_k^\prime=\alpha_k\oplus{}\gamma_k
% \label{eq:oplus}
% \end{equation}
% where the $\oplus{}$ denotes the operation of the Klein group; see Figure
% \ref{tab:1} for a detailed description. 
% \par
% }}}
% Espacio vectorial {{{

It will be useful to think of the multi-index $\valpha$ as an element of 
a vector space. To do so, we notice that any group with the property that
$\alpha \oplus \alpha =0$ is indeed a vector space under the two-element field
$\{0,1\}$\cite{alguna:referencia}. 
We notice that the Klein group described in \fref{tab:1} is actually isomorphic
to the two dimensional vector space over the field of two elements $\{0,1\}$.
Then, we build the complete vector space,
with the same field, and defining $\valpha \oplus \vbeta = (\alpha_1 \oplus
\beta_1,\cdots, \alpha_N \oplus \beta_N)$
\footnote{
We can further \cpnote{desmechar} the vector space, by identifying each index
$\alpha \in \{0,1,2,3\}$ with its binary notation [e.g. identify $2$ with $(1,0)$]
such that to each multindex  $\valpha$ there corresponds a binary string of 
length $2N$. In fact, our sum $\oplus$ would correspond to addition modulo 2 of 
each of the $2N$ components. 
}. 
We can indeed restate \eref{eq:oplus}, and say that for valid quantum channels, 
if $\tau_{\vec\alpha}=1$, then
$\tau_{\vec\gamma}=\tau_{\vec\alpha\oplus{}\vec\gamma}$.
For example, in \fref{fig:two:qubit:examples}(c) the indices that 
correspond to preserved components are 
$\valpha^{(0)} = (0,0)$, 
$\valpha^{(1)} = (0,2)$, 
$\valpha^{(2)} = (1,0)$, 
$\valpha^{(3)} = (2,2)$, and
$\valpha^{(4)} = (3,2)$. However, 
$\valpha^{(1)} + \valpha^{(2)} = (1,2)$, which is not preserved and thus this 
diagram does not correspond to a quantum channel.  From this view 
we can derive several interesting observations that will be presented in 
the rest of the section.
